The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-05-22 ms.Rmd

```{r plotzoonoverview, echo = FALSE, fig.show = 'hide', fig.height = 9, dpi = 300}

# four panel plot
par(mfrow = c(2, 2))

# plot the saved image in the first panel
library(raster)
r <- brick('figs/workflow_basic.png')
par(mar = c(1, 1, 2, 1))
plotRGB(r, maxpixels = Inf)

# add a panel letter
# this is an awful hack and completely contingent on the screenshot size :/
text(40, 940, labels = LETTERS[1],
      xpd = NA,
     cex = 1.2)

par(mar = c(1, 1, 2, 1))
# placeholder plots for each panel
for (i in 2:4) {

  # set up plotting window
  plot.new()
  plot.window(0:1, 0:1)

  # grey rectangle (no background in vector pdf?)
  rect(-1, -1, 2, 2, col = grey(0.9), border = NA)

  # text over the top
  text(0.5, 0.5, 'PLACEHOLDER',
       col = grey(0.3),
       cex = -13,
       xpd = NA)

  # add a panel letter
  mtext(text = LETTERS[i],
        side = 3,
        line = 0.5,
        adj = 0)  
}
```
![The modular SDM structure encoded by a zoon workflow. A) Flow diagram representing the module types. B) The required inputs and outputs for each module types (full details given in the `zoon` vignette 'Building a module'). C) Chaining and listing modules of the same type. D) The structure of a workflow object.\label{fig:workflows}](./figs/plotzoonoverview-1.png)

@@

```{r merowworkflow, eval = TRUE}
Merow_Silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = CarolinaWrenRasters,
    process = Background(n = 10000),
    model = list(LogisticRegression, MaxEnt, MaxLike),
    output = Chain(PerformanceMeasures, PrintMap))
```

>>>>

<!--
the figures for this panel are generated in powerpoint (I know, I know, but it's quick and easy) and saved in the figs folder.
the powerpoint file itself is not version controlled, but can be access here: https://www.dropbox.com/s/afjpv8v6na9y56e/diagrams.pptx?dl=0
-->

![The modular SDM structure encoded by a zoon workflow. A) Flow diagram representing the five module types and intermediate objects: df - an occurrence dataframe; ras - a RasterStack object; mod - a ZoonModel object; ? - any user-defined inputs or outputs. B) The flow diagram implied by chaining modules of the same type. C) The flow diagram implied by listing modules of the same type. Full details of module inputs and outputs, and the effects of listing and chaining each module type are given in the `zoon` vignette 'Building a module'. \label{fig:workflows}](./figs/diagrams.png)

@@

```{r merowworkflowtemp, eval = TRUE}
Merow_Silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = CarolinaWrenRasters,
    process = Background(n = 10000),
    model = list(LogisticRegression, MaxEnt, MaxLike),
    output = Chain(PerformanceMeasures, PrintMap))
```
